---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `strutilities`

<!-- badges: start -->
<!-- badges: end -->

The goal of `strutilities` is to perform obscure string manipulations.

## Installation

You can install the development version of strutilities like so:

``` r
install.packages('pak')
pak::pak('mjfrigaard/strutilities')
```

## Functions

`strutilities` has three functions (`sep_cols_mult()`, `process_text()` and `pivot_term_long()`). 

```{r example}
library(strutilities)
```

Each function has been written in base R (to keep dependencies low).

## sep_cols_mult()

```{r}
d <- data.frame(value = c(29L, 91L, 39L, 28L, 12L),
                full_name = c("John", "John, Jacob",
                         "John, Jacob, Jingleheimer",
                         "Jingleheimer, Schmidt",
                         "JJJ, Schmidt"))
d
sep_cols_mult(data = d, col = "full_name", col_prefix = "name")
```

## process_text()

```{r}
names(datasets::iris)
names(process_text(datasets::iris))
```

```{r}
str(datasets::InsectSprays)
str(process_text(datasets::InsectSprays, fct = TRUE))
```

## pivot_term_long()

```{r}
pivot_term_long("A large size in stockings is hard to sell.")
```

```{r}
terms <- c("A large size in stockings is hard to sell.", "The first part of the plan needs changing.")
pivot_term_long(terms)
```


